Host Galaxy Association for {\tt DIAObjects}

### 2020-04-21 draft-hostassoc.tex
stars excluded --> extended objects

For the ten\footnote{This is a conservative estimate.} {\tt Object} catalog galaxies (stars excluded) that are nearest to a given {\tt DIAObject} in terms of radial distance, a separation distance should be calculated with respect to the transient location using the second moments of each galaxy's luminosity profile (as described in Section \ref{sec:app}).

>>>>

For the ten\footnote{This is a conservative estimate.} {\tt Object} catalog galaxies (extended objects) that are nearest to a given {\tt DIAObject} in terms of radial distance, a separation distance should be calculated with respect to the transient location using the second moments of each galaxy's luminosity profile (as described in Section \ref{sec:app}).
